---
title: "Buckingham_HW27"
author: "May"
date: "11/13/2022"
output: html_document
---

Chapter 2 
```{r}
library(ggplot2)
mpg
```
lets do 5 functions to get more info about the dataset
```{r}
ggplot(mpg, aes(x = displ, y = hwy)) + 
  geom_point()
```
These plots show a correlation, as engine size increases, mileage decreases.

Make a boxplot for year and mpg for city driving
```{r}
ggplot(mpg, aes(x = year, y = cty)) + geom_boxplot()

```

```{r}
summary(mpg)
```
```{r}
ggplot(mpg, aes(cty, hwy)) + geom_point()
```
```{r}
ggplot(diamonds, aes(carat, price)) + geom_point()
```
Scatter plot

```{r}
ggplot(economics, aes(date, unemploy)) + geom_line()
```
Very cool line graph!

```{r}
ggplot(mpg, aes(cty)) + geom_histogram()
```
histogram

Now to add color, shape, and other aesthetic attributes
```{r}
aes(displ, hwy, colour = class) # you include it within the parenthesis after aes
```
```{r}
aes(displ, hwy, shape = drv)
```
```{r}
aes(displ, hwy, size = cyl)
```
```{r}
ggplot(mpg, aes(displ, hwy, colour = class)) + 
  geom_point() # you can use aesthetic to add outlying variables to the graph, in this examples were using color to ass class variable
```
To set an aesthetic to a fixed value, without scaling it, do so in the individual layer outside of aes()
```{r}
ggplot(mpg, aes(displ, hwy)) + geom_point(aes(colour = "blue"))
ggplot(mpg, aes(displ, hwy)) + geom_point(colour = "blue")
```
```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  facet_wrap(~class)
```

```{r}
geom_smooth()
```

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth() # adds a smoother line to the plot
```

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(span = 0.2) # span meeter controls the wiggliness of a line
```

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(span = 1) # bigger number = more smooth
```

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(span = 2)
```

```{r}
library(mgcv)
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(method = "gam", formula = y ~ s(x)) # gam fits a generalised additive model
```

```{r}
ggplot(mpg, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(method = "lm") #lm fits a linear model
```

```{r}
ggplot(mpg, aes(drv, hwy)) + 
  geom_point()
```
this causes a lot of overplotting

Jittering, geom_jitter(), adds a little random noise to the data which can help avoid overplotting.

Boxplots, geom_boxplot(), summarise the shape of the distribution with a handful of summary statistics.

Violin plots, geom_violin(), show a compact representation of the “density” of the distribution, highlighting the areas where more points are found.

```{r}
ggplot(mpg, aes(drv, hwy)) + geom_jitter()
ggplot(mpg, aes(drv, hwy)) + geom_boxplot()
ggplot(mpg, aes(drv, hwy)) + geom_violin()
```

histograms

```{r}
ggplot(mpg, aes(hwy)) + geom_histogram() #bars
ggplot(mpg, aes(hwy)) + geom_freqpoly() #lines
```

```{r}
# it is good to test out different bin widths before choosing
ggplot(mpg, aes(hwy)) + 
  geom_freqpoly(binwidth = 2.5)
ggplot(mpg, aes(hwy)) + 
  geom_freqpoly(binwidth = 1)
```

```{r}
# adding color is helpful in comparing distributions
ggplot(mpg, aes(displ, colour = drv)) + 
  geom_freqpoly(binwidth = 0.5)
ggplot(mpg, aes(displ, fill = drv)) + 
  geom_histogram(binwidth = 0.5) + 
  facet_wrap(~drv, ncol = 1)
```
Bar charts

```{r}
ggplot(mpg, aes(manufacturer)) + 
  geom_bar()
```

```{r}
drugs <- data.frame(
  drug = c("a", "b", "c"),
  effect = c(4.2, 9.7, 6.1))
```

```{r}
ggplot(drugs, aes(drug, effect)) + geom_bar(stat = "identity")
ggplot(drugs, aes(drug, effect)) + geom_point()

```
```{r}
ggplot(economics, aes(date, unemploy / pop)) +
  geom_line()
ggplot(economics, aes(date, uempmed)) +
  geom_line()
```

Now to draw both the series in the same plot
We'll do this by froming a path plot
We'll plot unemployment rate vs. length of unemployment and join the individual observations with a path. In the second plot, we color the points to make it easier to see the direction of time.
```{r}
ggplot(economics, aes(unemploy / pop, uempmed)) + 
  geom_path() +
  geom_point()

year <- function(x) as.POSIXlt(x)$year + 1900
ggplot(economics, aes(unemploy / pop, uempmed)) + 
  geom_path(colour = "grey50") +
  geom_point(aes(colour = year(date)))
```

xlab() and ylab() modify the x- and y-axis labels:
```{r}
ggplot(mpg, aes(cty, hwy)) +
  geom_point(alpha = 1 / 3)

ggplot(mpg, aes(cty, hwy)) +
  geom_point(alpha = 1 / 3) + 
  xlab("city driving (mpg)") + 
  ylab("highway driving (mpg)")

# Remove the axis labels with NULL
ggplot(mpg, aes(cty, hwy)) +
  geom_point(alpha = 1 / 3) + 
  xlab(NULL) + 
  ylab(NULL)
```
xlim() and ylim() modify the limits of axes:
```{r}
ggplot(mpg, aes(drv, hwy)) +
  geom_jitter(width = 0.25)

ggplot(mpg, aes(drv, hwy)) +
  geom_jitter(width = 0.25) + 
  xlim("f", "r") + 
  ylim(20, 30)
#> Warning: Removed 140 rows containing missing values (geom_point).
  
# For continuous scales, use NA to set only one limit
ggplot(mpg, aes(drv, hwy)) +
  geom_jitter(width = 0.25, na.rm = TRUE) + 
  ylim(NA, 30)
```

Output
```{r}
p <- ggplot(mpg, aes(displ, hwy, colour = factor(cyl))) +
  geom_point() # create a plot
```

view it with print()
```{r}
print(p)
```
```{r}
# Save png to disk
ggsave("plot.png", p, width = 5, height = 5)
```

summarise it
```{r}
summary(p)
```

save a copy 
```{r}
saveRDS(p, "plot.rds")
q <- readRDS("plot.rds")
```


