---
title: "Buckingham_HW23"
author: "May"
date: "10/25/2022"
output: html_document
---
Your data folder in this project does not contain any data so I cannot run your code. I'm taking off 0.5 points.

Your code looks good, but may not all work and I can't tell without running it.


Clear R's brain
```{r}
rm(list=ls())
library(dplyr)
library(here)
library(ggplot2)
```

Insert soil data 
```{r}
soil <- read.csv(here("soil_data.csv"))
View(soil)
```
make a scatterplot of the soil data for the SOM_percent column
```{r}
ggplot(soil, aes(x = Field.Name, y = SOM_percent)) + geom_point(size =5)+
xlab("Field Name") +
ylab("Soil Organic Matter %")
```
Now lets create a boxplot for the same variable
```{r}
ggplot(soil, aes(x = "11/17", y = SOM_percent)) + geom_boxplot()+
xlab("Date") +
ylab("Soil Organic Matter %")
```

Now lets make a histogram of the SOM_percent
```{r}
ggplot(soil, aes(x = SOM_percent)) + geom_histogram(bins = 10)
ggplot(soil, aes(x = SOM_percent)) + geom_histogram(binwidth = 15)+
  xlab("Soil Organic Matter %")
```
Now lets make a scatter plot for Ca PPM at each sample site
```{r}
ggplot(soil, aes(x = Field.Name, y = Ca.ppm)) + geom_point(size =5)+
xlab("Field Name") +
ylab("Soil Calcium PPM")

```
Now lets create the box plot for this data
```{r}
ggplot(soil, aes(x = "11/17", y = Ca.ppm)) + geom_boxplot()+
xlab("Date") +
ylab("Soil Calcium PPM")
```
Now lets create the histogram for this data
```{r}
ggplot(soil, aes(x = Ca.ppm)) + geom_histogram(bins = 10)
ggplot(soil, aes(x = Ca.ppm)) + geom_histogram(binwidth = 15)+
  xlab("Soil Calcium PPM")
```
Save, commit and push to github

