---
title: "Buckingham-Chapter4"
author: "May"
date: "10/20/2022"
output: html_document
---

Clear rs brain and add packages

```{r}
rm(list=ls())
library(dplyr)
library(here)
library(ggplot2)
```

Add compensation data into r and view it
```{r}
compensation <-read.csv(here("Data", "compensation.csv"))
View(compensation)
```
# Plotting basics with chapter 4!
#here is my script

#lets plot the data and add a theme at the end!
# we can increase the size of the points by saying "size = " in the () after geom_point
# we can modify the axis labels by adding xlab() and ylab()
# we can add color to plots by adding "colour = whatever variable" if you wanted a variable to be shown as a shape you would put "shape" instead of "colour"
```{r}
ggplot(compensation, aes(x = Root, y = Fruit, colour = Grazing)) + geom_point(size = 5) + xlab("Root Biomass") +
ylab("Fruit Production") + theme_bw()
```
#Now lets focus on how fuit production varies for each grazing treatment
# we can add raw data as it own layer by 
```{r}
ggplot(compensation, aes(x = Grazing, y = Fruit)) + geom_boxplot() + geom_point(size = 4, colour = 'lightgrey', alpha = 0.5) +
xlab("Grazing treatment") +
ylab("Fruit Production") +
theme_bw()
```
Now lets plot distributions by making a histogram of the fruit production
```{r}
ggplot(compensation, aes(x = Fruit)) + geom_histogram(bins = 10)
ggplot(compensation, aes(x = Fruit)) + geom_histogram(binwidth = 15)
# to make this look better we changed the binwidth and the number of bins

```

Now lets create a facet, or a structured matrix of graphs
facet_wrap is used to select the treatment, and ggplot divides the data into two graphs

```{r}
ggplot(compensation, aes(x = Fruit)) + geom_histogram(binwidth = 15) + facet_wrap(~Grazing)
```
Now lets save the data 
```{r}
ggsave("ThatCoolHistogramOfFruit.png")
```

Commit 

