---
title: "Buckingham_HW25"
author: "May"
date: "11/1/2022"
output: html_document
---

Clear R's brain
```{r}
rm(list=ls())
library(dplyr)
library(here)
library(ggplot2)
```

Insert the data and view it
```{r}
plantgr <- read.csv("plant.growth.rate.csv")
glimpse(plantgr)
```
This shows there are 2 variables, lets make a scatterplot to show this
```{r}
ggplot(plantgr, aes(x = soil.moisture.content, y = plant.growth.rate)) +
  geom_point() +
  ylab("Plant Growth Rate (mm/week)") + theme_bw()
```
Lets interpret this, the gradient is positive, the more moisture in the soil, the higher the plant growth rate.

Lets make a simple linear regression
```{r}
modelpgr <- lm(plant.growth.rate ~ soil.moisture.content, data = plantgr)
```
 Lets make diagnostic plots
```{r}
library(ggfortify)
autoplot(modelpgr, smooth.colour = NA)
```
nice
Top right:
it tells us whether a line is appropriate to fit to the data
Top Left:
This evaluates the assumption of normality of the residuals
Bottom right:
This evaluates the assumption of equal variance.
Bottom Left:
Evaluates leverege and detects outliers

Lets use anova() to produce the sums of squares table
```{r}
anova(modelpgr)
```
Now the summary table
```{r}
summary(modelpgr)

```
Lets put this back into our figure of the raw data
```{r}
ggplot(plantgr, aes(x = soil.moisture.content, y = plant.growth.rate)) +
geom_point() +
geom_smooth(method = 'lm') + ylab("Plant Growth Rate (mm/week)") + theme_bw()
  
```

Lets get a new dataset
```{r}
daphnia <-read.csv("Daphniagrowth.csv")
glimpse(daphnia)
```
Lets make a boxplot of the data in this set
```{r}
ggplot(daphnia, aes(x = parasite, y = growth.rate)) + geom_boxplot() +
theme_bw()
```
Now lets switch the coordinates
```{r}
ggplot(daphnia, aes(x = parasite, y = growth.rate)) + geom_boxplot() +
theme_bw() +
coord_flip()
```
Now lets create a linear regression model
```{r}
model_grow <- lm(growth.rate ~ parasite, data = daphnia)
```

lets plot the four diagnostic graphs
```{r}
autoplot(model_grow, smooth.colour = NA)

```
lets do anova() on this
```{r}
anova(model_grow)
```
Now summarize it
```{r}
summary(model_grow)
```
Save and commit to git hub

 
