---
title: "Buckingham_Homework19"
author: "May"
date: "10/16/2022"
output: html_document
---

##Homework-19
# In this homework we will examine a data set and fix any errors within the set so that R Studio can understand it. Then we will create a new data set and a histogram using the new data set
First we will clear the brain and add some packages. 
```{r}
rm(list=ls())
library(dplyr)
library(here)
library(ggplot2)
```

Now we will import the dataset with stringsAsFactors = TRUE

```{r}
Leaves <- read.csv(here("Data", "Class_leaf_measurements.csv"), stringsAsFactors = TRUE)
Leaves
```
Now lets examine to dataset
```{r}
str(Leaves)
```
```{r}
names(Leaves)

```
Now lets change the column names so that there are no spaces ir special characters

```{r}
Leaves <- Leaves %>% rename(DBH_cm = DBH..cm., Leaf_num = Leaf.., Petiole_Length = Petiole.length)
```
Now change the species names so that there are only three possibilities, Red Maple, Sugar Maple, and Norway Maple.
```{r}
RedMaple <- which(Leaves$Species == "red maple", Leaves$Species == "Red maple")
SugarMaple <- which(Leaves$Species == "Sugar maple", Leaves$Species == "sugar maple")
NorwayMaple <- which(Leaves$Species == "Norway maple")
```

I will create a new dataset called "Sugar" by selecting only the sugar maple data from the Leaves data set
```{r}
Sugar <-filter(Leaves, Species == "Sugar Maple" | Species == "sugar maple")
```
Now I will subset the columns in Sugar using the select function to leave outthe Person, Leaf number and Tree number variables. 
```{r}
Sugar <-select(Sugar, -Person, -Leaf_num, -Tree_num)
```
Now I will create a histogram of the data in the Sugar dataset
```{r}
hist(Sugar$Petiole_Length, main ="Histogram of Sugar Maple Petiole Lengths")
```


